---
title: "r5"
author: "Ruslan Basyrov"
date: "8/22/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
options(java.parameters = "-Xmx16G")
```

```{r}
library(r5r)
library(sf)
library(data.table)
library(ggplot2)
```

```{r}
year = 2022

# change the pathname
points <- read_sf(sprintf("/Users/johnnymosby/repos/thesis_demography/municipalitiesOSRMDistances/clientR/data/STATISTIK_AUSTRIA_GEM_MP_%s0101/", year),
                    options = "ENCODING=WINDOWS-1252")

points <- st_transform(points, 4326)

coordinates <- st_coordinates(points[, "geometry"]) |>
  as.data.frame()
coordinates$id = points$g_id

coordinates = coordinates[, c("id", "Y", "X")]
colnames(coordinates) = c("id", "lat", "lon")
```

```{r}
# change the pathname
data_path <- "/Users/johnnymosby/repos/thesis_demography/municipalitiesR5Distances/files/"
```

### Setting up the routing machine of R5
```{r}
r5r_core <- setup_r5(data_path = data_path)
```

### A bit about time window
The time window is 3 hours between 17:00 and 20:00. The distances are calculated for each minute within the time window. Then the smallest value is taken as representing the time distances between the points. The assumption is that people are rational and do not wait for the public transport unnecessarily.
```{r}
mode <- c("WALK", "TRANSIT")
max_walk_time <- 120 # minutes
max_trip_duration <- 120 # minutes
departure_datetime <- as.POSIXct("24-08-2024 17:00:00",
                                 format = "%d-%m-%Y %H:%M:%S")

ttm <- expanded_travel_time_matrix(r5r_core = r5r_core,
                          origins = coordinates,
                          destinations = coordinates,
                          mode = mode,
                          departure_datetime = departure_datetime,
                          max_trip_duration = max_trip_duration,
                          max_walk_time = max_walk_time,
                          time_window = 180,
                          progress = TRUE)

ttm <- ttm[
    , .SD[which.min(get('total_time'))],
                    by = .(from_id, to_id)
    ][
        , .(from_id, to_id, total_time)
    ]

head(ttm)
```

```{r}
result <- dcast(ttm, from_id ~ to_id, value.var = "total_time")

rownames(result) = result$from_id
result[, from_id := NULL]
```

### Ugly runarounds between the differences of data.table and data.frame tables.
```{r}
result[row(result) == col(result)] <- 0

result[1, 1] = 10101
setnames(result, "from_id", "")

datetime = format(Sys.time(), "%Y%m%d_%H%M")

write.csv(result, paste("output/durations_", datetime, ".csv", sep = ""), sep = ",")
```

